%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{%
    Thomas~C.~M.~Lee \\
    Department of Statistics \\
    University of California, Davis  \\
    4118 Math Sci Bldg, One Shields Ave  \\
    Davis, CA 95616
}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Dr.~Charles~R.~Hogg~III \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Google, Inc. \\ 6425 Penn Avenue \#700 \\ Pittsburgh, PA 15206 \\ (412) 449-9111 % Your address and phone number
\\ \texttt{chogg@google.com}
\end{center} 
\vfill

\signature{Charles~R.~Hogg~III} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Dr.~Lee,} 

I wish to submit the attached paper, ``Visualizing uncertain curves and surfaces via Gaussian Oscillators,'' for consideration to be published in the \textit{Journal of Computational and Graphical Statistics}.
The paper contains 5 figures, 5862 words, and no tables.
A great many papers published in this journal deal with curves or surfaces which have uncertainty (for instance, papers on topics such as regression or Gaussian Processes).
This uncertainty is highly challenging to visualize, but my paper presents several advancements.
Therefore, I believe it will be of great interest to this journal's readership.

The paper contains several novel and useful results, of which I emphasize the following.
It is the first paper to investigate the statistical properties of \textit{individual} animations, rather than \textit{populations} of animations.
(This is critically important, since real visualizations typically contain only a single animation.)
It also introduces a novel animation technique, whose motion is more fluid and natural, and whose animation frames are all on equal footing (no special ``keyframes'' are singled out).
Finally, it paves the way for future developments, by identifying these animations as a special class of Gaussian Process (which I have called ``Gaussian oscillators'' for ease of reference).

Allow me to suggest several reviewers who I expect will find my work useful, and who will be able to critique it in detail.
Philipp Hennig (\texttt{phennig@tuebingen.mpg.de}) has used animations to teach Gaussian Processes in summer and winter school sessions since 2013.
John Skilling (\texttt{skilling@eircom.net}) developed the first statistically correct animation technique in 1991.
Charles Ehlschlaeger (\texttt{ehlschl1@illinois.edu}), Ashton Shortridge (\texttt{ashton@msu.edu}), and Michael Goodchild (\texttt{good@geog.ucsb.edu}) applied Dr. Skilling's technique to elevation data in a highly cited paper from 1997.

I confirm that this manuscript has been submitted solely to the journal and that it is not published, in press, or submitted elsewhere.
I confirm that this research complies with all relevant ethical guidelines and legal requirements.
I confirm that I have prepared the complete text of the paper, that I am the sole author, and that I have seen, read, and understood your guidelines on copyright.
Finally, I confirm that I have no conflict of interest.

Thank you very much for your time and consideration.
I look forward to hearing back from you.

\closing{Sincerely yours,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
